---
title: "Mini Project 2"
author: "Rachel Aliwalas"
date: "12/2/2021"
output: pdf_document
---

```{r, include=FALSE, wanring=FALSE}
library(tidyverse)
library(readr)

mp2_data <- read_csv("/home/rba/SDS290/MP2/MiniProject2.csv")
```


```{r}
clean_data <- mp2_data %>%
  slice(3:79) %>% 
  select(stayed_longer, familiarity, danceability, song) %>% 
  filter(danceability != "NA")
```


#exploring data

```{r}
qplot(x = song, y = as.numeric(danceability), data = clean_data, geom = "boxplot") + labs(x = "Speed of Song", y = "Danceability", title = "Figure 1: Boxplots of the Danceability of across the Song's BPM")
```

```{r}
ggplot(clean_data, aes(x = interaction(song, familiarity), y = danceability)) + 
  geom_boxplot()#THIS LOOKS WACKED LMAO
```

```{r}
#ggplot(clean_data, aes(x = song, y = danceability, fill = familiarity)) +
 # geom_boxplot()
```


```{r}
ggplot(clean_data, aes(x = song, y = danceability, color = familiarity)) +
  geom_point()
```


```{r}
ds <- clean_data %>% 
  group_by(as.factor(song)) %>% 
  mutate(danceability = as.numeric(danceability)) %>% 
  summarize(n = n(), 
            m = mean(danceability),
            sd = sd(danceability))
ds

ds %>% 
  ungroup() %>%
  summarise(max(sd)/min(sd))
```

difference in sd's are small enough for us to continue


# Formal Analysis

Run two-way ANOVA without the interaction term using the original data.

null hyp: the group means are the same
alt hyp: group means are different


```{r}
mod1 <- lm(danceability ~ song + familiarity, data = clean_data)

anova(mod1)
```


## Interactions

Check for interactions: Create an interaction plot.

```{r}
ggplot(clean_data, aes(x = song, y = danceability, 
                    group = familiarity, 
                    color = familiarity)) +
  geom_point() +
  geom_smooth(method = "lm", se = 0)
```

Conduct a two-way ANOVA

```{r}
mod2 <- lm(danceability ~ song * familiarity, data = clean_data)

anova(mod2)
```


song and dancability - there are statistically significant differences in group means
familiarity and danceability - there are statistically significant differences in group means

interaction is insignificant



# Residual Analysis 

Check conditions on the residuals

```{r}
qplot(x = mod2$residuals, bins = 5)
plot(mod2, which = 2)
plot(mod2, which = 1)
```

# Confidence intervals and effect sizes

```{r} 
#need to fix for our own values
SD = sqrt(36.25) 
t = qt(.975, 8)

#Conditional averages
mean_B12_antiNO <- 22 - 19

mean_B12_antiYES <- 54 - 3

LL_B12_antiNO = mean_B12_antiNO - SD*t*sqrt(1/3+1/3)
UL_B12_antiNO = mean_B12_antiNO + SD*t*sqrt(1/3+1/3)

LL_B12_antiYES = mean_B12_antiYES - SD*t*sqrt(1/3+1/3)
UL_B12_antiYES = mean_B12_antiYES + SD*t*sqrt(1/3+1/3)

LL_B12_antiNO
UL_B12_antiNO

LL_B12_antiYES
UL_B12_antiYES
```

```{r}
mean_B12_antiNO/SD
mean_B12_antiYES/SD
```


